### 2023-12-22 thesis/MSECE_thesis.tex
Added input representations and training objective section for the ASR models.

Although the internal processing of data varies between architectures, the format of the models input and output is the same for the models described
below. ASR models have seen much success and performance gains for speech-related tasks such as speech and speaker recognition through the use of
Mel-frequency Cepstral Coefficients (MFCCs) \cite{sahidullah_design_2012}. Since ASR is not the main focus of this thesis, the process for computing
the MFCCs will only be described from a high level as it is described in \cite{sahidullah_design_2012}. Readers should refer to
\cite{sahidullah_design_2012} for a more detailed, matrix-based approach for computing MFCCs. Given an audio signal:

@@

\noindent
The MFCCs are then used as input to the ASR models. Each model outputs a probability distribution of characters or tokens (depending on the vocabulary
the ASR model is initialized with) over a segment of audio. All the ASR models used are trained with a Connectionist Temporal Classification (CTC)
loss function~\cite{graves_connectionist_2006}.

>>>>

\subsection{Input Representation}\label{sec:asr_input_representation}
Although the internal processing of data varies between architectures, the format of the models input and output is the same for the models described
below. ASR models have seen much success and performance gains for speech-related tasks such as speech and speaker recognition through the use of
Mel-frequency Cepstral Coefficients (MFCCs) \cite{sahidullah_design_2012}. Since ASR is not the main focus of this thesis, the process for computing
the MFCCs will only be described from a high level as it is described in \cite{sahidullah_design_2012}. Readers should refer to
\cite{sahidullah_design_2012} for a more detailed, matrix-based approach for computing MFCCs. Given an audio signal:

@@

\noindent
The MFCCs are then used as input to the ASR models. Each model outputs a probability distribution of characters or tokens (depending on the vocabulary
the ASR model is initialized with) over a segment of audio.

\subsection{Training Objective}\label{sec:asr_training_objective}
The ASR models listed below both use a Connectionist Temporal Classification (CTC) training objective \cite{graves_connectionist_2006}. For a
dataset, $D$, made up of inputs and labels, $x$ and $y$, respectively.

\begin{equation}\label{eq:ctc_dataset}
    D = \{(x_1, y_1), (x_2, y_2), ..., (x_N, y_N)\}
\end{equation}

\noindent
Where $N$ is the number of samples in the dataset, $D$. The goal of the ASR model training procedure is to predict the target, $y$, based on the input
sequence, $x$. This can also be written as maximizing the likelihood of $p(y|x)$. More formally, the CTC objective function can be written as

\begin{equation}\label{eq:ctc_objective}
    O^{ML}(D, \mathcal{N}) = - \sum_{(x,y) \in D} \ln p(y|x)
\end{equation}

\noindent
where $\mathcal{N}$ is the network being optimized to maximize the likelihood of predicting $p(y|x)$. Put simply, the goal of the ASR network is to
maximize the log-likelihood of predicting a label, $y$, given an input, $x$.

The novelty of the CTC objective is in the fact that the audio signal does not need to be segmented in order to label and train a network. Instead,
the output layer of the network has $L + 1$ units, where $L$ is the alphabet/vocabulary of the network. At each time step in the audio signal, the
network will predict either a token from its vocabulary or a blank token, hence the extra unit in the output layer. Repeated predictions and blank
tokens are removed from the prediction, then scored against the ground truth label for the audio signal \cite{graves_connectionist_2006}.
